---
title : "`r substr(toupper(params$opco), 1, 2)`"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    navbar:
      - { title: "Data Catalog", href: "http://report.grandvision.global/bi-doc/udc", align: right }
    orientation: columns
    vertical_layout: fill
params:
  denv : "prd"    # environment acc | prd
  opco : "ch"     # 2 character opco
<<<<<<< HEAD
  nrws : "Inf"    # c(-1,0,1,n)
=======
  nrws : "Inf"        # c(-1,0,1,n)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
---

```{r setup, include=FALSE}
# this file sources all other scripts
source(file.path("~", "isdb", "00-scripts", "00_setup.R"))
<<<<<<< HEAD
opco_labels <- f_read_opco_labels()
=======

scipen <- options("scipen")[["scipen"]]
options(scipen = 999)

>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
```

```{r read_data, eval=TRUE}
system.time({
  
# read nrows from all tables 
raw_data <-
  f_read_opco_data(
    denv = params$denv,                    # environment acc | prd
<<<<<<< HEAD
    opco = params$opco,                    # 2 character opco    
#    ds   = c("ARTICLE"),                   # specific Data Sources
=======
    opco = params$opco,                    # 2 character opco
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
    nrws = as.numeric(params$nrws)         # c(-1,0,1,n)
  ) 

})


# SO <- raw_data[["SELL_OUT"]][, .(Q = sum(QUANTITY)), by = .(LOCAL_ARTICLE_ID)]
# 
# ARTICLE_FRAME_AND_SUN <- 
#   SO[ARTICLE_FRAME_AND_SUN, on = .(LOCAL_ARTICLE_ID),
#      nomatch = 0]


# write.csv2(
#   ARTICLE_FRAME_AND_SUN, 
#   paste0("../60-results/", params$opco, "_articleQ.csv"))


# raw_data[["SELL_OUT"]] <- 
#   ARTICLE_FRAME_AND_SUN[raw_data[["SELL_OUT"]], 
#                         on = .(LOCAL_ARTICLE_ID), nomatch = 0] %>%
#   .[, `:=` (Purchase_Price       = COGS/QUANTITY,
#             Retail_Price_inc_VAT = GROSS_VALUE_SALES_INC_VAT/QUANTITY,
#             Retail_Price_ex_VAT  = GROSS_VALUE_SALES_EX_VAT/QUANTITY)] 
# # %>%
# #   .[ISVALID                == 1  &
# #       RETURN_INDICATOR       == "0" &
# #       CANCELLATION_INDICATOR == "0", ]
# 
# raw_data[["DISCOUNTS"]] <- 
#   raw_data[["DISCOUNTS"]][raw_data[["SELL_OUT"]],
#                           on = .(LINK_TO_TICKET_ID_LINE == TICKET_ID_LINE,
#                                  STORE_ID, TICKET_ID)]

# read metadata_didp
metadata_didp <-
  f_read_meta_data(opco = params$opco)     # 2 character opco

<<<<<<< HEAD

```

```{r determine_factors, eval=F}

# Check Primary Keys
primary_key <- 
  f_check_primkeys(
    lst_raw_data     = raw_data,
    dt_metadata_didp = metadata_didp
  )

f_write_primary_key_log(primary_key)

raw_data <- 
  f_remove_duplicates(
    primary_key = primary_key,
    lst_raw_data = raw_data
  )




# TAB <- "ARTICLE"
# 
# system.time(
#   tst3 <- f_analyze_tables(raw_data[TAB])
#   )
# 
# dtDSTATS <- 
#   lapply(names(tst3[[TAB]]), f_get_column_analysis, 
#          .lst= tst3, .table = TAB, .resultset = "DSTATS") %>% 
#   rbindlist() %>%
#   .[, SOURCE := TAB]


```

```{r graph_purchase-price, eval=FALSE}
x <- 
  raw_data[["SELL_OUT"]] %>%
  .[, .(Category = factor(CATEGORY_NAME), PP = COGS/QUANTITY)] %>% 
  .[PP <= 0, PP:= 0.01 ] %>%
  .[is.nan(PP) , PP:= 0.01 ]

gvColors <- 
  c(GV_BLUE_0, GV_ORNG_0)

names(gvColors) <- 
  levels(x$Category)

colScale <- 
  scale_fill_manual(name = "Category", values = gvColors)

p1 <- 
  ggplot(data = x, 
         mapping = aes(x = Category, y = PP, 
                       fill = Category))
(p2 <- 
  p1 + 
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + 
  scale_y_log10(breaks = c(0.1, 10, 50, 100, 500, 1000, 10000)) + 
  colScale +
  labs(x = "Category", y = "Purchase price"))
```

ISVALID == 1 & RETURN_INDICATOR == 0 & CANCELLATION_INDICATOR == 0

```{r graph_gan_mapping, eval=FALSE}
path <- 
  file.path("..", "80-figures", "pmdm_mapping") %>%
  f_get_folder()

# inner-join frame & Sun and add MD attributes
x <- 
  raw_data[["SELL_OUT"]] %>%
  ARTICLE_FRAME_AND_SUN[, .(LOCAL_ARTICLE_ID, CATEGORY_CODE, MAP) ][
    ., on = .(LOCAL_ARTICLE_ID), nomatch = 0 ] %>%
  .[, .(Q = sum(QUANTITY), V = sum(GROSS_VALUE_SALES_INC_VAT)), 
    by = .(Month    = floor_date(ymd(DATE), "month"), 
           Category = factor(
             CATEGORY_CODE, labels = c("Frames", "Sunglasses")), 
           MAP)] 

# map the GV-colors 
#                    "-"      , MARA_EAN , PMDM_EAN , PMDM_GAN
gvColors        <- c(GV_ORNG_0, GV_GREY_1, GV_BLUE_2, GV_BLUE_0)
names(gvColors) <- levels(x$MAP)
colScale        <- scale_fill_manual(name = "pmdm", values = gvColors)
colScale_col    <- scale_color_manual(name = "pmdm", values = gvColors)

# Determine the breaks
db <- paste(ceiling(length(unique(x$Month))/9), "month")
br <- (1:10)/10
et <- element_text(
      family = "DejaVu Sans", face = "plain", colour = GV_GREY_1, size = 15)
at <- element_text(
      family = "DejaVu Sans", face = "plain", colour = GV_GREY_1, size = 12)

# Map data, aesthetics, GV colors and time scale
pQ <- 
  ggplot(data = x, mapping = aes(x = Month, y = Q, fill = MAP)) +
  colScale + 
  scale_x_date(date_breaks = eval(db), date_labels = "%Y.%m") +
  scale_y_continuous(sec.axis = sec_axis(~ . )) +
  # labs(title = paste0(params$opco ), x = "Date") +
  labs(
    title = opco_labels[OPCO == params$opco, LABEL], 
    subtitle = format(today(), "%A, %d %B, %Y "),
    x = "Date") +  
  facet_wrap(facets = "Category", nrow = 2) +
  theme(text = at, title = et, legend.position = "bottom")

# Plot Identity
(pQI <- 
    pQ + 
    geom_col() +                             # legend.position="top"
    # geom_hline(
    #   data = x[, .(yintercept = mean(Q)), by = .(Category, MAP)], 
    #   mapping= aes(yintercept = yintercept, color = MAP)) +
    # colScale_col +
    labs(y = "Sell-Out Vol. ")
  ) 
# save plot per day
ggsave(plot = pQI, 
       file.path(path, paste0(params$opco, "_qi_", today(), ".png")))

x_mean_cumQ <- 
  copy(x) %>%
  .[, .(tot = sum(Q)), by = .(Category, MAP)] %>%
  .[, yintercept:= tot/sum(tot), by = .(Category)] %T>%
  setorder(Category, -MAP) %>%
  .[, yintercept:=cumsum(yintercept), by = .(Category)]

# Plot Percentage 
(pQP <- pQ + geom_col(position = position_fill())  + 
    labs(y = "Sell-Out Vol. % ") +
    geom_hline(
      data = x_mean_cumQ, 
      mapping= aes(yintercept = yintercept, color = MAP), linetype = "dashed", size = 1) +
    colScale_col +
    scale_y_continuous(
      labels = scales::percent_format(), breaks = br,
  sec.axis = sec_axis(~ ., labels = scales::percent_format(), breaks = br )))
# save plot per day
ggsave(plot = pQP, 
       file.path(path, paste0(params$opco, "_qp_", today(), ".png")))

pV <- 
  ggplot(data = x, mapping = aes(x = Month, y = V, fill = MAP)) +
  colScale + 
  scale_x_date(date_breaks = eval(db), date_labels = "%Y.%m") +
  scale_y_continuous(sec.axis = sec_axis(~ . )) +  
  # labs(title = paste0(params$opco ), x = "Date") +
  labs(
    title = opco_labels[OPCO == params$opco, LABEL], 
    subtitle = format(today(), "%A, %d %B, %Y "),
    x = "Date") +    
  facet_wrap(facets = "Category", nrow = 2) +
  theme(text = at, title = et, legend.position = "bottom")

# Plot Identity
(pVI <- pV + geom_col() + labs(y = "Sell-Out Val. "))   
# save plot per day
ggsave(plot = pVI, 
       file.path(path, paste0(params$opco, "_vi_", today(), ".png")))

x_mean_cumV <- 
  copy(x) %>%
  .[, .(tot = sum(V)), by = .(Category, MAP)] %>%
  .[, yintercept:= tot/sum(tot), by = .(Category)] %T>%
  setorder(Category, -MAP) %>%
  .[, yintercept:=cumsum(yintercept), by = .(Category)]

# Plot Percentage 
(pVP <- pV + geom_col(position = position_fill())  + 
    labs(y = "Sell-Out Val. % ") +    
    geom_hline(
      data = x_mean_cumV, 
      mapping= aes(yintercept = yintercept, color = MAP), linetype = "dashed", size = 1) +
    colScale_col +    
    scale_y_continuous(
      labels = scales::percent_format(), breaks = br,
      sec.axis = sec_axis(~ ., labels = scales::percent_format(), breaks = br )))
# save plot per day
ggsave(plot = pVP, 
       file.path(path, paste0(params$opco, "_vp_", today(), ".png")))
```

```{r global_article_mapping, eval=TRUE}
metadata_didp[COLUMN_NAME == "GLOBAL_ARTICLE_NUMBER", DS] %>%
  f_write_global_article_log(raw_data = raw_data)
=======
})
```

```{r determine_factors}

system.time(
  tst <- f_analyze_tables(raw_data["SELL_OUT"])
  )

dtDSTATS <- 
  lapply(names(tst[["SELL_OUT"]]), f_get_column_analysis, 
         .lst= tst, .table = "SELL_OUT", .resultset = "DSTATS") %>% 
  rbindlist() %>%
  .[, SOURCE := "SELL_OUT"]

>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
```

```{r process_tables, eval=TRUE}

f_process_factors <- 
  function(x){
    
    output <- list()    

    output[["value"]]   <- lapply(x, f_get_value)
    output[["pattern"]] <- lapply(x, f_get_pattern)
    output[["word"]]    <- lapply(x, f_get_word)
    output
  }

# output[['store']][['pattern']][['STORE_ID']]
output <- lapply(opco_factors, f_process_factors)
#cardin <- lapply(raw_data, f_calc_cardinality)

```

# Article { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Article_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Article_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Article_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# Discounts { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Discounts_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Discounts_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Discounts_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# Sell_in { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Sell_in_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Sell_in_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Sell_in_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# Sell_out { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Sell_out_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Sell_out_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Sell_out_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# Stock { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Stock_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Stock_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Stock_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# Store { data-orientation=rows }

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)

## Overview

### PMDM

> ToDo: link to PMDM ID

```{r Store_gauge_pmdm}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Emerald

> ToDo: link to Emerald Store ID

```{r Store_gauge_emerald}
rate <- 50
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

### Vacant

> ToDo: relevant key field to be linked

```{r Store_gauge_vacant}
rate <- 20
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
  href = "#Details"
)
```

## Comments

### Action Points {data-width=1200}


### Comments

- bullet points or table 



# article_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)

## 

### Meta Data 
Table: **`r toupper("article")`**

```{r article_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("article"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# discounts_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)

## 

### Meta Data 
Table: **`r toupper("discounts")`**

```{r discounts_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("discounts"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# sell_in_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)

## 

### Meta Data 
Table: **`r toupper("sell_in")`**

```{r sell_in_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("sell_in"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# sell_out_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)

## 

### Meta Data 
Table: **`r toupper("sell_out")`**

```{r sell_out_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("sell_out"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# stock_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)

## 

### Meta Data 
Table: **`r toupper("stock")`**

```{r stock_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("stock"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# store_columns_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)

## 

### Meta Data 
Table: **`r toupper("store")`**

```{r store_columns_description}
# Show metadata of OPCO-table

knitr::kable(
  metadata_didp[
    DS == toupper("store"), 
    !c("ID", "IMPORT", "OPCO", "TABLE_NAME", "DS")])


```

# Article_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)

## 

### Basic Statistics

```{r Article_basic_statistics}
 knitr::kable(cardin[[toupper('Article')]])  
```

# Discounts_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)

## 

### Basic Statistics

```{r Discounts_basic_statistics}
 knitr::kable(cardin[[toupper('Discounts')]])  
```

# Sell_in_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)

## 

### Basic Statistics

```{r Sell_in_basic_statistics}
 knitr::kable(cardin[[toupper('Sell_in')]])  
```

# Sell_out_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)

## 

### Basic Statistics

```{r Sell_out_basic_statistics}
 knitr::kable(cardin[[toupper('Sell_out')]])  
```

# Stock_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)

## 

### Basic Statistics

```{r Stock_basic_statistics}
 knitr::kable(cardin[[toupper('Stock')]])  
```

# Store_basic_statistics {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)

## 

### Basic Statistics

```{r Store_basic_statistics}
 knitr::kable(cardin[[toupper('Store')]])  
```

# article_category_code {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### category_code
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_category_code_value}
  output[[toupper('article')]][['value']][[toupper('category_code')]]
```
    
### Pattern 
  
```{r article_category_code_pattern}
  output[[toupper('article')]][['pattern']][[toupper('category_code')]]
```
  
### Word
  
```{r article_category_code_word}
  output[[toupper('article')]][['word']][[toupper('category_code')]]
```

# article_category_name {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### category_name
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_category_name_value}
  output[[toupper('article')]][['value']][[toupper('category_name')]]
```
    
### Pattern 
  
```{r article_category_name_pattern}
  output[[toupper('article')]][['pattern']][[toupper('category_name')]]
```
  
### Word
  
```{r article_category_name_word}
  output[[toupper('article')]][['word']][[toupper('category_name')]]
```

# article_global_article_number {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### global_article_number
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_global_article_number_value}
  output[[toupper('article')]][['value']][[toupper('global_article_number')]]
```
    
### Pattern 
  
```{r article_global_article_number_pattern}
  output[[toupper('article')]][['pattern']][[toupper('global_article_number')]]
```
  
### Word
  
```{r article_global_article_number_word}
  output[[toupper('article')]][['word']][[toupper('global_article_number')]]
```

# article_local_article_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### local_article_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_local_article_id_value}
  output[[toupper('article')]][['value']][[toupper('local_article_id')]]
```
    
### Pattern 
  
```{r article_local_article_id_pattern}
  output[[toupper('article')]][['pattern']][[toupper('local_article_id')]]
```
  
### Word
  
```{r article_local_article_id_word}
  output[[toupper('article')]][['word']][[toupper('local_article_id')]]
```

# article_local_ean {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### local_ean
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_local_ean_value}
  output[[toupper('article')]][['value']][[toupper('local_ean')]]
```
    
### Pattern 
  
```{r article_local_ean_pattern}
  output[[toupper('article')]][['pattern']][[toupper('local_ean')]]
```
  
### Word
  
```{r article_local_ean_word}
  output[[toupper('article')]][['word']][[toupper('local_ean')]]
```

# article_opco {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### opco
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_opco_value}
  output[[toupper('article')]][['value']][[toupper('opco')]]
```
    
### Pattern 
  
```{r article_opco_pattern}
  output[[toupper('article')]][['pattern']][[toupper('opco')]]
```
  
### Word
  
```{r article_opco_word}
  output[[toupper('article')]][['word']][[toupper('opco')]]
```

# article_product_brand {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### product_brand
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_product_brand_value}
  output[[toupper('article')]][['value']][[toupper('product_brand')]]
```
    
### Pattern 
  
```{r article_product_brand_pattern}
  output[[toupper('article')]][['pattern']][[toupper('product_brand')]]
```
  
### Word
  
```{r article_product_brand_word}
  output[[toupper('article')]][['word']][[toupper('product_brand')]]
```

# article_product_name {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### product_name
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_product_name_value}
  output[[toupper('article')]][['value']][[toupper('product_name')]]
```
    
### Pattern 
  
```{r article_product_name_pattern}
  output[[toupper('article')]][['pattern']][[toupper('product_name')]]
```
  
### Word
  
```{r article_product_name_word}
  output[[toupper('article')]][['word']][[toupper('product_name')]]
```

# article_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_ssis_log_lastupdate_value}
  output[[toupper('article')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r article_ssis_log_lastupdate_pattern}
  output[[toupper('article')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r article_ssis_log_lastupdate_word}
  output[[toupper('article')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# article_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_ssislogid_value}
  output[[toupper('article')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r article_ssislogid_pattern}
  output[[toupper('article')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r article_ssislogid_word}
  output[[toupper('article')]][['word']][[toupper('ssislogid')]]
```

# article_supplier_name {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#article)  

[Meta Data](#article_columns_description)

[Basic Statistics](#article_basic_statistics)


- [CATEGORY_CODE](#article_category_code)
- [CATEGORY_NAME](#article_category_name)
- [GLOBAL_ARTICLE_NUMBER](#article_global_article_number)
- [LOCAL_ARTICLE_ID](#article_local_article_id)
- [LOCAL_EAN](#article_local_ean)
- [OPCO](#article_opco)
- [PRODUCT_BRAND](#article_product_brand)
- [PRODUCT_NAME](#article_product_name)
- [SSISLOGID](#article_ssislogid)
- [SSIS_LOG_LASTUPDATE](#article_ssis_log_lastupdate)
- [SUPPLIER_NAME](#article_supplier_name)
    
## Graphs {.tabset .tabset-fade}
    
### supplier_name
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r article_supplier_name_value}
  output[[toupper('article')]][['value']][[toupper('supplier_name')]]
```
    
### Pattern 
  
```{r article_supplier_name_pattern}
  output[[toupper('article')]][['pattern']][[toupper('supplier_name')]]
```
  
### Word
  
```{r article_supplier_name_word}
  output[[toupper('article')]][['word']][[toupper('supplier_name')]]
```

# discounts_currency {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### currency
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_currency_value}
  output[[toupper('discounts')]][['value']][[toupper('currency')]]
```
    
### Pattern 
  
```{r discounts_currency_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('currency')]]
```
  
### Word
  
```{r discounts_currency_word}
  output[[toupper('discounts')]][['word']][[toupper('currency')]]
```

# discounts_discount_item_description {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### discount_item_description
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_discount_item_description_value}
  output[[toupper('discounts')]][['value']][[toupper('discount_item_description')]]
```
    
### Pattern 
  
```{r discounts_discount_item_description_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('discount_item_description')]]
```
  
### Word
  
```{r discounts_discount_item_description_word}
  output[[toupper('discounts')]][['word']][[toupper('discount_item_description')]]
```

# discounts_discount_item_ex_vat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### discount_item_ex_vat
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# discounts_discount_item_inc_vat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### discount_item_inc_vat
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# discounts_discount_item_key {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### discount_item_key
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_discount_item_key_value}
  output[[toupper('discounts')]][['value']][[toupper('discount_item_key')]]
```
    
### Pattern 
  
```{r discounts_discount_item_key_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('discount_item_key')]]
```
  
### Word
  
```{r discounts_discount_item_key_word}
  output[[toupper('discounts')]][['word']][[toupper('discount_item_key')]]
```

# discounts_isvalid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### isvalid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_isvalid_value}
  output[[toupper('discounts')]][['value']][[toupper('isvalid')]]
```
    
### Pattern 
  
```{r discounts_isvalid_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('isvalid')]]
```
  
### Word
  
```{r discounts_isvalid_word}
  output[[toupper('discounts')]][['word']][[toupper('isvalid')]]
```

# discounts_link_to_ticket_id_line_seq {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### link_to_ticket_id_line_seq
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_link_to_ticket_id_line_seq_value}
  output[[toupper('discounts')]][['value']][[toupper('link_to_ticket_id_line_seq')]]
```
    
### Pattern 
  
```{r discounts_link_to_ticket_id_line_seq_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('link_to_ticket_id_line_seq')]]
```
  
### Word
  
```{r discounts_link_to_ticket_id_line_seq_word}
  output[[toupper('discounts')]][['word']][[toupper('link_to_ticket_id_line_seq')]]
```

# discounts_link_to_ticket_id_line {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### link_to_ticket_id_line
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_link_to_ticket_id_line_value}
  output[[toupper('discounts')]][['value']][[toupper('link_to_ticket_id_line')]]
```
    
### Pattern 
  
```{r discounts_link_to_ticket_id_line_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('link_to_ticket_id_line')]]
```
  
### Word
  
```{r discounts_link_to_ticket_id_line_word}
  output[[toupper('discounts')]][['word']][[toupper('link_to_ticket_id_line')]]
```

# discounts_salesorg {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### salesorg
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_salesorg_value}
  output[[toupper('discounts')]][['value']][[toupper('salesorg')]]
```
    
### Pattern 
  
```{r discounts_salesorg_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('salesorg')]]
```
  
### Word
  
```{r discounts_salesorg_word}
  output[[toupper('discounts')]][['word']][[toupper('salesorg')]]
```

# discounts_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_ssis_log_lastupdate_value}
  output[[toupper('discounts')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r discounts_ssis_log_lastupdate_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r discounts_ssis_log_lastupdate_word}
  output[[toupper('discounts')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# discounts_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_ssislogid_value}
  output[[toupper('discounts')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r discounts_ssislogid_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r discounts_ssislogid_word}
  output[[toupper('discounts')]][['word']][[toupper('ssislogid')]]
```

# discounts_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_store_id_value}
  output[[toupper('discounts')]][['value']][[toupper('store_id')]]
```
    
### Pattern 
  
```{r discounts_store_id_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('store_id')]]
```
  
### Word
  
```{r discounts_store_id_word}
  output[[toupper('discounts')]][['word']][[toupper('store_id')]]
```

# discounts_ticket_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#discounts)  

[Meta Data](#discounts_columns_description)

[Basic Statistics](#discounts_basic_statistics)


- [CURRENCY](#discounts_currency)
- [DISCOUNT_ITEM_DESCRIPTION](#discounts_discount_item_description)
- [DISCOUNT_ITEM_KEY](#discounts_discount_item_key)
- [ISVALID](#discounts_isvalid)
- [LINK_TO_TICKET_ID_LINE](#discounts_link_to_ticket_id_line)
- [LINK_TO_TICKET_ID_LINE_SEQ](#discounts_link_to_ticket_id_line_seq)
- [SALESORG](#discounts_salesorg)
- [SSISLOGID](#discounts_ssislogid)
- [SSIS_LOG_LASTUPDATE](#discounts_ssis_log_lastupdate)
- [STORE_ID](#discounts_store_id)
- [TICKET_ID](#discounts_ticket_id)
- [DISCOUNT_ITEM_EX_VAT](#discounts_discount_item_ex_vat)
- [DISCOUNT_ITEM_INC_VAT](#discounts_discount_item_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ticket_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r discounts_ticket_id_value}
  output[[toupper('discounts')]][['value']][[toupper('ticket_id')]]
```
    
### Pattern 
  
```{r discounts_ticket_id_pattern}
  output[[toupper('discounts')]][['pattern']][[toupper('ticket_id')]]
```
  
### Word
  
```{r discounts_ticket_id_word}
  output[[toupper('discounts')]][['word']][[toupper('ticket_id')]]
```

# sell_in_currency {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### currency
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_currency_value}
  output[[toupper('sell_in')]][['value']][[toupper('currency')]]
```
    
### Pattern 
  
```{r sell_in_currency_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('currency')]]
```
  
### Word
  
```{r sell_in_currency_word}
  output[[toupper('sell_in')]][['word']][[toupper('currency')]]
```

# sell_in_date {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### date
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_date_value}
  output[[toupper('sell_in')]][['value']][[toupper('date')]]
```
    
### Pattern 
  
```{r sell_in_date_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('date')]]
```
  
### Word
  
```{r sell_in_date_word}
  output[[toupper('sell_in')]][['word']][[toupper('date')]]
```

# sell_in_global_article_number {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### global_article_number
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_global_article_number_value}
  output[[toupper('sell_in')]][['value']][[toupper('global_article_number')]]
```
    
### Pattern 
  
```{r sell_in_global_article_number_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('global_article_number')]]
```
  
### Word
  
```{r sell_in_global_article_number_word}
  output[[toupper('sell_in')]][['word']][[toupper('global_article_number')]]
```

# sell_in_isvalid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### isvalid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_isvalid_value}
  output[[toupper('sell_in')]][['value']][[toupper('isvalid')]]
```
    
### Pattern 
  
```{r sell_in_isvalid_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('isvalid')]]
```
  
### Word
  
```{r sell_in_isvalid_word}
  output[[toupper('sell_in')]][['word']][[toupper('isvalid')]]
```

# sell_in_local_article_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### local_article_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_local_article_id_value}
  output[[toupper('sell_in')]][['value']][[toupper('local_article_id')]]
```
    
### Pattern 
  
```{r sell_in_local_article_id_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('local_article_id')]]
```
  
### Word
  
```{r sell_in_local_article_id_word}
  output[[toupper('sell_in')]][['word']][[toupper('local_article_id')]]
```

# sell_in_net_purchase_value {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### net_purchase_value
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_in_opco {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### opco
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_opco_value}
  output[[toupper('sell_in')]][['value']][[toupper('opco')]]
```
    
### Pattern 
  
```{r sell_in_opco_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('opco')]]
```
  
### Word
  
```{r sell_in_opco_word}
  output[[toupper('sell_in')]][['word']][[toupper('opco')]]
```

# sell_in_quantity {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### quantity
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_in_return_indicator {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### return_indicator
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_in_salesorg {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### salesorg
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_salesorg_value}
  output[[toupper('sell_in')]][['value']][[toupper('salesorg')]]
```
    
### Pattern 
  
```{r sell_in_salesorg_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('salesorg')]]
```
  
### Word
  
```{r sell_in_salesorg_word}
  output[[toupper('sell_in')]][['word']][[toupper('salesorg')]]
```

# sell_in_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_ssis_log_lastupdate_value}
  output[[toupper('sell_in')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r sell_in_ssis_log_lastupdate_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r sell_in_ssis_log_lastupdate_word}
  output[[toupper('sell_in')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# sell_in_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_ssislogid_value}
  output[[toupper('sell_in')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r sell_in_ssislogid_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r sell_in_ssislogid_word}
  output[[toupper('sell_in')]][['word']][[toupper('ssislogid')]]
```

# sell_in_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_store_id_value}
  output[[toupper('sell_in')]][['value']][[toupper('store_id')]]
```
    
### Pattern 
  
```{r sell_in_store_id_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('store_id')]]
```
  
### Word
  
```{r sell_in_store_id_word}
  output[[toupper('sell_in')]][['word']][[toupper('store_id')]]
```

# sell_in_time {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### time
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_time_value}
  output[[toupper('sell_in')]][['value']][[toupper('time')]]
```
    
### Pattern 
  
```{r sell_in_time_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('time')]]
```
  
### Word
  
```{r sell_in_time_word}
  output[[toupper('sell_in')]][['word']][[toupper('time')]]
```

# sell_in_warehouse_site {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_in)  

[Meta Data](#sell_in_columns_description)

[Basic Statistics](#sell_in_basic_statistics)


- [CURRENCY](#sell_in_currency)
- [DATE](#sell_in_date)
- [GLOBAL_ARTICLE_NUMBER](#sell_in_global_article_number)
- [ISVALID](#sell_in_isvalid)
- [LOCAL_ARTICLE_ID](#sell_in_local_article_id)
- [OPCO](#sell_in_opco)
- [SALESORG](#sell_in_salesorg)
- [SSISLOGID](#sell_in_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_in_ssis_log_lastupdate)
- [STORE_ID](#sell_in_store_id)
- [TIME](#sell_in_time)
- [WAREHOUSE_SITE](#sell_in_warehouse_site)
- [QUANTITY](#sell_in_quantity)
<<<<<<< HEAD
=======
- [RETURN_INDICATOR](#sell_in_return_indicator)
- [SSISLOGID](#sell_in_ssislogid)
- [TIME](#sell_in_time)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [NET_PURCHASE_VALUE](#sell_in_net_purchase_value)
    
## Graphs {.tabset .tabset-fade}
    
### warehouse_site
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_in_warehouse_site_value}
  output[[toupper('sell_in')]][['value']][[toupper('warehouse_site')]]
```
    
### Pattern 
  
```{r sell_in_warehouse_site_pattern}
  output[[toupper('sell_in')]][['pattern']][[toupper('warehouse_site')]]
```
  
### Word
  
```{r sell_in_warehouse_site_word}
  output[[toupper('sell_in')]][['word']][[toupper('warehouse_site')]]
```

# sell_out_cancellation_indicator {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### cancellation_indicator
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_cogs {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### cogs
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_consumer_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### consumer_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_consumer_id_value}
  output[[toupper('sell_out')]][['value']][[toupper('consumer_id')]]
```
    
### Pattern 
  
```{r sell_out_consumer_id_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('consumer_id')]]
```
  
### Word
  
```{r sell_out_consumer_id_word}
  output[[toupper('sell_out')]][['word']][[toupper('consumer_id')]]
```

# sell_out_currency {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### currency
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_currency_value}
  output[[toupper('sell_out')]][['value']][[toupper('currency')]]
```
    
### Pattern 
  
```{r sell_out_currency_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('currency')]]
```
  
### Word
  
```{r sell_out_currency_word}
  output[[toupper('sell_out')]][['word']][[toupper('currency')]]
```

# sell_out_date_delivered {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### date_delivered
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_date_delivered_value}
  output[[toupper('sell_out')]][['value']][[toupper('date_delivered')]]
```
    
### Pattern 
  
```{r sell_out_date_delivered_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('date_delivered')]]
```
  
### Word
  
```{r sell_out_date_delivered_word}
  output[[toupper('sell_out')]][['word']][[toupper('date_delivered')]]
```

# sell_out_date {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### date
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_date_value}
  output[[toupper('sell_out')]][['value']][[toupper('date')]]
```
    
### Pattern 
  
```{r sell_out_date_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('date')]]
```
  
### Word
  
```{r sell_out_date_word}
  output[[toupper('sell_out')]][['word']][[toupper('date')]]
```

# sell_out_global_article_number {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### global_article_number
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_global_article_number_value}
  output[[toupper('sell_out')]][['value']][[toupper('global_article_number')]]
```
    
### Pattern 
  
```{r sell_out_global_article_number_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('global_article_number')]]
```
  
### Word
  
```{r sell_out_global_article_number_word}
  output[[toupper('sell_out')]][['word']][[toupper('global_article_number')]]
```

# sell_out_gross_value_sales_ex_vat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### gross_value_sales_ex_vat
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_gross_value_sales_inc_vat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### gross_value_sales_inc_vat
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_isvalid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### isvalid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_isvalid_value}
  output[[toupper('sell_out')]][['value']][[toupper('isvalid')]]
```
    
### Pattern 
  
```{r sell_out_isvalid_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('isvalid')]]
```
  
### Word
  
```{r sell_out_isvalid_word}
  output[[toupper('sell_out')]][['word']][[toupper('isvalid')]]
```

# sell_out_local_article_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### local_article_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_local_article_id_value}
  output[[toupper('sell_out')]][['value']][[toupper('local_article_id')]]
```
    
### Pattern 
  
```{r sell_out_local_article_id_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('local_article_id')]]
```
  
### Word
  
```{r sell_out_local_article_id_word}
  output[[toupper('sell_out')]][['word']][[toupper('local_article_id')]]
```

# sell_out_quantity {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### quantity
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_return_indicator {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### return_indicator
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# sell_out_salesorg {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### salesorg
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_salesorg_value}
  output[[toupper('sell_out')]][['value']][[toupper('salesorg')]]
```
    
### Pattern 
  
```{r sell_out_salesorg_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('salesorg')]]
```
  
### Word
  
```{r sell_out_salesorg_word}
  output[[toupper('sell_out')]][['word']][[toupper('salesorg')]]
```

# sell_out_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_ssis_log_lastupdate_value}
  output[[toupper('sell_out')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r sell_out_ssis_log_lastupdate_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r sell_out_ssis_log_lastupdate_word}
  output[[toupper('sell_out')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# sell_out_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_ssislogid_value}
  output[[toupper('sell_out')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r sell_out_ssislogid_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r sell_out_ssislogid_word}
  output[[toupper('sell_out')]][['word']][[toupper('ssislogid')]]
```

# sell_out_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_store_id_value}
  output[[toupper('sell_out')]][['value']][[toupper('store_id')]]
```
    
### Pattern 
  
```{r sell_out_store_id_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('store_id')]]
```
  
### Word
  
```{r sell_out_store_id_word}
  output[[toupper('sell_out')]][['word']][[toupper('store_id')]]
```

# sell_out_ticket_id_line {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ticket_id_line
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_ticket_id_line_value}
  output[[toupper('sell_out')]][['value']][[toupper('ticket_id_line')]]
```
    
### Pattern 
  
```{r sell_out_ticket_id_line_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('ticket_id_line')]]
```
  
### Word
  
```{r sell_out_ticket_id_line_word}
  output[[toupper('sell_out')]][['word']][[toupper('ticket_id_line')]]
```

# sell_out_ticket_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### ticket_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_ticket_id_value}
  output[[toupper('sell_out')]][['value']][[toupper('ticket_id')]]
```
    
### Pattern 
  
```{r sell_out_ticket_id_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('ticket_id')]]
```
  
### Word
  
```{r sell_out_ticket_id_word}
  output[[toupper('sell_out')]][['word']][[toupper('ticket_id')]]
```

# sell_out_time {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#sell_out)  

[Meta Data](#sell_out_columns_description)

[Basic Statistics](#sell_out_basic_statistics)


<<<<<<< HEAD
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
=======
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [CURRENCY](#sell_out_currency)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [GLOBAL_ARTICLE_NUMBER](#sell_out_global_article_number)
- [ISVALID](#sell_out_isvalid)
- [LOCAL_ARTICLE_ID](#sell_out_local_article_id)
- [SALESORG](#sell_out_salesorg)
- [SSISLOGID](#sell_out_ssislogid)
- [SSIS_LOG_LASTUPDATE](#sell_out_ssis_log_lastupdate)
- [STORE_ID](#sell_out_store_id)
- [TICKET_ID](#sell_out_ticket_id)
- [TICKET_ID_LINE](#sell_out_ticket_id_line)
- [TIME](#sell_out_time)
<<<<<<< HEAD
- [QUANTITY](#sell_out_quantity)
=======
- [CANCELLATION_INDICATOR](#sell_out_cancellation_indicator)
- [CONSUMER_ID](#sell_out_consumer_id)
- [DATE](#sell_out_date)
- [DATE_DELIVERED](#sell_out_date_delivered)
- [ISVALID](#sell_out_isvalid)
- [QUANTITY](#sell_out_quantity)
- [RETURN_INDICATOR](#sell_out_return_indicator)
- [SSISLOGID](#sell_out_ssislogid)
>>>>>>> 13b56439ffaaea014c6891c97e012f380c83d9fa
- [COGS](#sell_out_cogs)
- [GROSS_VALUE_SALES_EX_VAT](#sell_out_gross_value_sales_ex_vat)
- [GROSS_VALUE_SALES_INC_VAT](#sell_out_gross_value_sales_inc_vat)
    
## Graphs {.tabset .tabset-fade}
    
### time
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r sell_out_time_value}
  output[[toupper('sell_out')]][['value']][[toupper('time')]]
```
    
### Pattern 
  
```{r sell_out_time_pattern}
  output[[toupper('sell_out')]][['pattern']][[toupper('time')]]
```
  
### Word
  
```{r sell_out_time_word}
  output[[toupper('sell_out')]][['word']][[toupper('time')]]
```

# stock_currency {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### currency
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_currency_value}
  output[[toupper('stock')]][['value']][[toupper('currency')]]
```
    
### Pattern 
  
```{r stock_currency_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('currency')]]
```
  
### Word
  
```{r stock_currency_word}
  output[[toupper('stock')]][['word']][[toupper('currency')]]
```

# stock_date {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### date
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_date_value}
  output[[toupper('stock')]][['value']][[toupper('date')]]
```
    
### Pattern 
  
```{r stock_date_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('date')]]
```
  
### Word
  
```{r stock_date_word}
  output[[toupper('stock')]][['word']][[toupper('date')]]
```

# stock_global_article_number {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### global_article_number
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_global_article_number_value}
  output[[toupper('stock')]][['value']][[toupper('global_article_number')]]
```
    
### Pattern 
  
```{r stock_global_article_number_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('global_article_number')]]
```
  
### Word
  
```{r stock_global_article_number_word}
  output[[toupper('stock')]][['word']][[toupper('global_article_number')]]
```

# stock_local_article_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### local_article_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_local_article_id_value}
  output[[toupper('stock')]][['value']][[toupper('local_article_id')]]
```
    
### Pattern 
  
```{r stock_local_article_id_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('local_article_id')]]
```
  
### Word
  
```{r stock_local_article_id_word}
  output[[toupper('stock')]][['word']][[toupper('local_article_id')]]
```

# stock_opco {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### opco
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_opco_value}
  output[[toupper('stock')]][['value']][[toupper('opco')]]
```
    
### Pattern 
  
```{r stock_opco_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('opco')]]
```
  
### Word
  
```{r stock_opco_word}
  output[[toupper('stock')]][['word']][[toupper('opco')]]
```

# stock_quantity {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### quantity
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# stock_site {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### site
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_site_value}
  output[[toupper('stock')]][['value']][[toupper('site')]]
```
    
### Pattern 
  
```{r stock_site_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('site')]]
```
  
### Word
  
```{r stock_site_word}
  output[[toupper('stock')]][['word']][[toupper('site')]]
```

# stock_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_ssis_log_lastupdate_value}
  output[[toupper('stock')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r stock_ssis_log_lastupdate_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r stock_ssis_log_lastupdate_word}
  output[[toupper('stock')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# stock_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_ssislogid_value}
  output[[toupper('stock')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r stock_ssislogid_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r stock_ssislogid_word}
  output[[toupper('stock')]][['word']][[toupper('ssislogid')]]
```

# stock_stock_status {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### stock_status
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_stock_status_value}
  output[[toupper('stock')]][['value']][[toupper('stock_status')]]
```
    
### Pattern 
  
```{r stock_stock_status_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('stock_status')]]
```
  
### Word
  
```{r stock_stock_status_word}
  output[[toupper('stock')]][['word']][[toupper('stock_status')]]
```

# stock_stock_value {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### stock_value
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# stock_time {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#stock)  

[Meta Data](#stock_columns_description)

[Basic Statistics](#stock_basic_statistics)


- [CURRENCY](#stock_currency)
- [DATE](#stock_date)
- [GLOBAL_ARTICLE_NUMBER](#stock_global_article_number)
- [LOCAL_ARTICLE_ID](#stock_local_article_id)
- [OPCO](#stock_opco)
- [SITE](#stock_site)
- [SSISLOGID](#stock_ssislogid)
- [SSIS_LOG_LASTUPDATE](#stock_ssis_log_lastupdate)
- [STOCK_STATUS](#stock_stock_status)
- [TIME](#stock_time)
- [QUANTITY](#stock_quantity)
- [STOCK_VALUE](#stock_stock_value)
    
## Graphs {.tabset .tabset-fade}
    
### time
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r stock_time_value}
  output[[toupper('stock')]][['value']][[toupper('time')]]
```
    
### Pattern 
  
```{r stock_time_pattern}
  output[[toupper('stock')]][['pattern']][[toupper('time')]]
```
  
### Word
  
```{r stock_time_word}
  output[[toupper('stock')]][['word']][[toupper('time')]]
```

# store_address_line_1 {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### address_line_1
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_address_line_1_value}
  output[[toupper('store')]][['value']][[toupper('address_line_1')]]
```
    
### Pattern 
  
```{r store_address_line_1_pattern}
  output[[toupper('store')]][['pattern']][[toupper('address_line_1')]]
```
  
### Word
  
```{r store_address_line_1_word}
  output[[toupper('store')]][['word']][[toupper('address_line_1')]]
```

# store_address_line_2 {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### address_line_2
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_address_line_2_value}
  output[[toupper('store')]][['value']][[toupper('address_line_2')]]
```
    
### Pattern 
  
```{r store_address_line_2_pattern}
  output[[toupper('store')]][['pattern']][[toupper('address_line_2')]]
```
  
### Word
  
```{r store_address_line_2_word}
  output[[toupper('store')]][['word']][[toupper('address_line_2')]]
```

# store_city {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### city
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_city_value}
  output[[toupper('store')]][['value']][[toupper('city')]]
```
    
### Pattern 
  
```{r store_city_pattern}
  output[[toupper('store')]][['pattern']][[toupper('city')]]
```
  
### Word
  
```{r store_city_word}
  output[[toupper('store')]][['word']][[toupper('city')]]
```

# store_date_closed {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### date_closed
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_date_closed_value}
  output[[toupper('store')]][['value']][[toupper('date_closed')]]
```
    
### Pattern 
  
```{r store_date_closed_pattern}
  output[[toupper('store')]][['pattern']][[toupper('date_closed')]]
```
  
### Word
  
```{r store_date_closed_word}
  output[[toupper('store')]][['word']][[toupper('date_closed')]]
```

# store_date_opened {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### date_opened
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_date_opened_value}
  output[[toupper('store')]][['value']][[toupper('date_opened')]]
```
    
### Pattern 
  
```{r store_date_opened_pattern}
  output[[toupper('store')]][['pattern']][[toupper('date_opened')]]
```
  
### Word
  
```{r store_date_opened_word}
  output[[toupper('store')]][['word']][[toupper('date_opened')]]
```

# store_emerald_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### emerald_store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_emerald_store_id_value}
  output[[toupper('store')]][['value']][[toupper('emerald_store_id')]]
```
    
### Pattern 
  
```{r store_emerald_store_id_pattern}
  output[[toupper('store')]][['pattern']][[toupper('emerald_store_id')]]
```
  
### Word
  
```{r store_emerald_store_id_word}
  output[[toupper('store')]][['word']][[toupper('emerald_store_id')]]
```

# store_predecessor_emerald_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### predecessor_emerald_store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_predecessor_emerald_store_id_value}
  output[[toupper('store')]][['value']][[toupper('predecessor_emerald_store_id')]]
```
    
### Pattern 
  
```{r store_predecessor_emerald_store_id_pattern}
  output[[toupper('store')]][['pattern']][[toupper('predecessor_emerald_store_id')]]
```
  
### Word
  
```{r store_predecessor_emerald_store_id_word}
  output[[toupper('store')]][['word']][[toupper('predecessor_emerald_store_id')]]
```

# store_predecessor_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### predecessor_store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_predecessor_store_id_value}
  output[[toupper('store')]][['value']][[toupper('predecessor_store_id')]]
```
    
### Pattern 
  
```{r store_predecessor_store_id_pattern}
  output[[toupper('store')]][['pattern']][[toupper('predecessor_store_id')]]
```
  
### Word
  
```{r store_predecessor_store_id_word}
  output[[toupper('store')]][['word']][[toupper('predecessor_store_id')]]
```

# store_region {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### region
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_region_value}
  output[[toupper('store')]][['value']][[toupper('region')]]
```
    
### Pattern 
  
```{r store_region_pattern}
  output[[toupper('store')]][['pattern']][[toupper('region')]]
```
  
### Word
  
```{r store_region_word}
  output[[toupper('store')]][['word']][[toupper('region')]]
```

# store_retail_surface_area {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### retail_surface_area
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# store_salesorg {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### salesorg
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_salesorg_value}
  output[[toupper('store')]][['value']][[toupper('salesorg')]]
```
    
### Pattern 
  
```{r store_salesorg_pattern}
  output[[toupper('store')]][['pattern']][[toupper('salesorg')]]
```
  
### Word
  
```{r store_salesorg_word}
  output[[toupper('store')]][['word']][[toupper('salesorg')]]
```

# store_ssis_log_lastupdate {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### ssis_log_lastupdate
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_ssis_log_lastupdate_value}
  output[[toupper('store')]][['value']][[toupper('ssis_log_lastupdate')]]
```
    
### Pattern 
  
```{r store_ssis_log_lastupdate_pattern}
  output[[toupper('store')]][['pattern']][[toupper('ssis_log_lastupdate')]]
```
  
### Word
  
```{r store_ssis_log_lastupdate_word}
  output[[toupper('store')]][['word']][[toupper('ssis_log_lastupdate')]]
```

# store_ssislogid {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### ssislogid
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_ssislogid_value}
  output[[toupper('store')]][['value']][[toupper('ssislogid')]]
```
    
### Pattern 
  
```{r store_ssislogid_pattern}
  output[[toupper('store')]][['pattern']][[toupper('ssislogid')]]
```
  
### Word
  
```{r store_ssislogid_word}
  output[[toupper('store')]][['word']][[toupper('ssislogid')]]
```

# store_store_cluster {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_cluster
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_store_cluster_value}
  output[[toupper('store')]][['value']][[toupper('store_cluster')]]
```
    
### Pattern 
  
```{r store_store_cluster_pattern}
  output[[toupper('store')]][['pattern']][[toupper('store_cluster')]]
```
  
### Word
  
```{r store_store_cluster_word}
  output[[toupper('store')]][['word']][[toupper('store_cluster')]]
```

# store_store_id {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_id
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_store_id_value}
  output[[toupper('store')]][['value']][[toupper('store_id')]]
```
    
### Pattern 
  
```{r store_store_id_pattern}
  output[[toupper('store')]][['pattern']][[toupper('store_id')]]
```
  
### Word
  
```{r store_store_id_word}
  output[[toupper('store')]][['word']][[toupper('store_id')]]
```

# store_store_lat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_lat
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# store_store_long {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_long
Gauges _key figures
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
# store_store_type_subcat {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_type_subcat
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_store_type_subcat_value}
  output[[toupper('store')]][['value']][[toupper('store_type_subcat')]]
```
    
### Pattern 
  
```{r store_store_type_subcat_pattern}
  output[[toupper('store')]][['pattern']][[toupper('store_type_subcat')]]
```
  
### Word
  
```{r store_store_type_subcat_word}
  output[[toupper('store')]][['word']][[toupper('store_type_subcat')]]
```

# store_store_type {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### store_type
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_store_type_value}
  output[[toupper('store')]][['value']][[toupper('store_type')]]
```
    
### Pattern 
  
```{r store_store_type_pattern}
  output[[toupper('store')]][['pattern']][[toupper('store_type')]]
```
  
### Word
  
```{r store_store_type_word}
  output[[toupper('store')]][['word']][[toupper('store_type')]]
```

# store_zip_code {.hidden data-orientation=rows}

## Navigation {.sidebar}

[Key Data Domain](#store)  

[Meta Data](#store_columns_description)

[Basic Statistics](#store_basic_statistics)


- [ADDRESS_LINE_1](#store_address_line_1)
- [ADDRESS_LINE_2](#store_address_line_2)
- [CITY](#store_city)
- [DATE_CLOSED](#store_date_closed)
- [DATE_OPENED](#store_date_opened)
- [EMERALD_STORE_ID](#store_emerald_store_id)
- [PREDECESSOR_EMERALD_STORE_ID](#store_predecessor_emerald_store_id)
- [PREDECESSOR_STORE_ID](#store_predecessor_store_id)
- [REGION](#store_region)
- [SALESORG](#store_salesorg)
- [SSISLOGID](#store_ssislogid)
- [SSIS_LOG_LASTUPDATE](#store_ssis_log_lastupdate)
- [STORE_CLUSTER](#store_store_cluster)
- [STORE_ID](#store_store_id)
- [STORE_TYPE](#store_store_type)
- [STORE_TYPE_SUBCAT](#store_store_type_subcat)
- [ZIP_CODE](#store_zip_code)
- [RETAIL_SURFACE_AREA](#store_retail_surface_area)
- [STORE_LAT](#store_store_lat)
- [STORE_LONG](#store_store_long)
    
## Graphs {.tabset .tabset-fade}
    
### zip_code
Gauges
  
### Comments

**todo:  **

- Text or table with findings
- special characters found?
- cardinality
  
### Histogram 
  
### BoxPlot
  
## Tables {.tabset .tabset-fade}
  
### Values 
    
```{r store_zip_code_value}
  output[[toupper('store')]][['value']][[toupper('zip_code')]]
```
    
### Pattern 
  
```{r store_zip_code_pattern}
  output[[toupper('store')]][['pattern']][[toupper('zip_code')]]
```
  
### Word
  
```{r store_zip_code_word}
  output[[toupper('store')]][['word']][[toupper('zip_code')]]
```

# Files {data-orientation=rows}

## {data-height=150}

### Data Profiling Dashboard 

**Generated on:** `r format(with_tz(Sys.time(), tzone = "Europe/Amsterdam" ), 
'%A, %B %d, %Y %X')`

## {data-height=900}

### Data Files

Information on data extracts

```{r display_file_info, eval=TRUE, echo=FALSE, results='asis'}

opco_path <- 
  file.path(p_raw, params$denv, f_get_opco_folder(params$opco))

dtFileInfo <- 
  f_get_file_info(opco_path, list.files(opco_path))                      %T>%
   # .[, age:= {interval(Sys.time(), mtime) %>% as.period() }]        %>%
  setorder(-mtime)  

knitr::kable(
  dtFileInfo[, .(Name = filename, Date = mtime, Size = size_unit)]
)
```

### Meta data

Information refresh of metadata

```{r get_meta_data_file_Info, eval=TRUE, echo=FALSE, results='asis'}

dt_meta_data_file_info <- 
  f_get_file_info(p_src, list.files(p_src))                              %T>%
  setorder(-mtime)  

 knitr::kable(
   dt_meta_data_file_info[, .(Name = filename, 
                              Date = mtime, Size = size_unit)])

```

