---
title: "PVC-BI"
output: 
  flexdashboard::flex_dashboard:
  # theme: journal
  theme: cosmo
navbar:
  - { title: "About", href: "https://www.grandvision.com", align: right }    
orientation: columns
vertical_layout: fill
logo: flex_gv.png
favicon: favicon.ico    
params:
  denv  : "prd"             # environment acc | prd
  opco  :                   # 2 character opco
  nrws  : "Inf"             # c(-1,0,1,n)
#    css: test.css    
---
  
```{r setup, include=FALSE}
library(flexdashboard)
source(file.path("~", "isdb", "00-scripts", "00_setup.R"))
pWidth <- .5

```

```{r create_graphs, eval=TRUE, include=FALSE}
opcos <- c("ch", "tr", "pe", "co", "it")

DT <- 
  f_get_opcos_sell_out_pmdm_mapping(
    opcos = opcos,
    pmdm_file_name = "20210118141218_PMDM_Full.csv")

lst <- 
  map(.x = opcos, f_create_igraph_gan_mapping, DT) %>%
  set_names(opcos)

```

# Swiss {data-navmenu="Opco" data-orientation=rows}
## {.tabset .tabset-fade}

### Volume 

```{r}
# add interactive bar -------
ggplotly(lst[["ch"]][["pQI"]])

```

### Volume % 

```{r}
# add interactive bar -------
ggplotly(lst[["ch"]][["pQP"]])
```
  
### Value 

```{r}
# add interactive bar -------
ggplotly(lst[["ch"]][["pVI"]])
```
  
### Value % 

```{r}
# add interactive bar -------
ggplotly(lst[["ch"]][["pVP"]])
```

# Turkey {data-navmenu="Opco" data-orientation=rows}
## {.tabset .tabset-fade}

### Volume 

```{r}
# add interactive bar -------
ggplotly(lst[["tr"]][["pQI"]])

```

### Volume % 

```{r}
# add interactive bar -------
ggplotly(lst[["tr"]][["pQP"]])
```
  
### Value 

```{r}
# add interactive bar -------
ggplotly(lst[["tr"]][["pVI"]])
```
  
### Value % 

```{r}
# add interactive bar -------
ggplotly(lst[["tr"]][["pVP"]])
```

# Peru {data-navmenu="Opco" data-orientation=rows}
## {.tabset .tabset-fade}

### Volume 

```{r}
# add interactive bar -------
ggplotly(lst[["pe"]][["pQI"]])

```

### Volume % 

```{r}
# add interactive bar -------
ggplotly(lst[["pe"]][["pQP"]])
```
  
### Value 

```{r}
# add interactive bar -------
ggplotly(lst[["pe"]][["pVI"]])
```
  
### Value % 

```{r}
# add interactive bar -------
ggplotly(lst[["pe"]][["pVP"]])
```

# Columbia {data-navmenu="Opco" data-orientation=rows}
## {.tabset .tabset-fade}

### Volume 

```{r}
# add interactive bar -------
ggplotly(lst[["co"]][["pQI"]])

```

### Volume % 

```{r}
# add interactive bar -------
ggplotly(lst[["co"]][["pQP"]])
```
  
### Value 

```{r}
# add interactive bar -------
ggplotly(lst[["co"]][["pVI"]])
```
  
### Value % 

```{r}
# add interactive bar -------
ggplotly(lst[["co"]][["pVP"]])
```

# Italy {data-navmenu="Opco" data-orientation=rows}
## {.tabset .tabset-fade}

### Volume 

```{r}
# add interactive bar -------
ggplotly(lst[["it"]][["pQI"]])

```

### Volume % 

```{r}
# add interactive bar -------
ggplotly(lst[["it"]][["pQP"]])
```
  
### Value 

```{r}
# add interactive bar -------
ggplotly(lst[["it"]][["pVI"]])
```
  
### Value % 

```{r}
# add interactive bar -------
ggplotly(lst[["it"]][["pVP"]])
```
