---
title: "PVC-BI"
output: 
  flexdashboard::flex_dashboard:
  # theme: journal
  theme: cosmo
navbar:
  - { title: "About", href: "https://www.grandvision.com", align: right }    
orientation: rows
# orientation: columns
logo: flex_gv.png
favicon: favicon.ico    
params:
  denv  : "prd"             # environment acc | prd
  opco  :                   # 2 character opco
  nrws  : "Inf"             # c(-1,0,1,n)
#    css: test.css    
---
  
```{r setup, include=FALSE}
library(flexdashboard)
source(file.path("~", "isdb", "00-scripts", "00_setup.R"))

```

```{r create_graphs, eval=TRUE, include=FALSE}
opcos <- c("pe")

DT <- 
  f_get_opcos_sell_out_pmdm_mapping(opcos = opcos)

lst <- f_create_igraph_gan_mapping(DT[OPCO == "pe"])

```

# OPCO {data-icon="far fa-building" .storyboard}

### **Sell-out Volume per month**. 
Blue is volume which can be related to PMDM, Orange can't as no valid GAN/EAN was provided {data-commentary-width=300} 
  
```{r}
# add interactive bar -------

(lst[["pQI"]])
```
  
*** 
**Sell-out Value per month**

- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
  
### **Sell-out Volume % per month**. 
Blue is volume which can be related to PMDM, Orange can't as no valid GAN/EAN was provided {data-commentary-width=300} 
  
```{r}
# add interactive bar -------

(lst[["pQP"]])
```
  
*** 
**Sell-out Volume % per month**

- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN

### **Sell-out Value per month**. 
Blue is volume which can be related to PMDM, Orange can't as no valid GAN/EAN was provided {data-commentary-width=300} 
  
```{r}
# add interactive bar -------

(lst[["pVI"]])
```
  
*** 
**Sell-out Value per month**

- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN  

### **Sell-out Value % per month**. 
Blue is volume which can be related to PMDM, Orange can't as no valid GAN/EAN was provided {data-commentary-width=300} 
  
```{r}
# add interactive bar -------

(lst[["pVP2"]])
```
  
*** 
**Sell-out Value % per month**

- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN
- 15% on average can be related to PMDM using GAN  


    
