---
title: "PVC-BI"
output: 
  flexdashboard::flex_dashboard:
  # theme: journal
  theme: cosmo
navbar:
  - { title: "About", href: "https://www.grandvision.com", align: right }    
orientation: rows
# orientation: columns
logo: flex_gv.png
favicon: favicon.ico    
params:
  denv : "prd"    # environment acc | prd
  opco : "ch"     # 2 character opco
  nrws : "Inf"    # c(-1,0,1,n)
#    css: test.css    
---
  
```{r setup, include=FALSE}
library(flexdashboard)
source(file.path("~", "isdb", "00-scripts", "00_setup.R"))
opco_labels <- f_read_opco_labels()
```

# Menu {.sidebar}

- [icon](#icon)
- [Profiling](http://www.kpn.com)
  
# icon {data-icon="far fa-building" .storyboard}
  
### Frame 0
  
[CSS](C:\Users\Floris\Documents\R\win-library\3.6\flexdashboard\rmarkdown\templates\flex_dashboard\resources)
  
"default", "cerulean", "journal", "flatly", "darkly", "readable", "spacelab", "united", "cosmo", "lumen", "paper", "sandstone", "simplex", "yeti"
  
  default
  X cosmo     hard blauw
  bootstrap   wit
  X cerulean  donker blauw  gauges te licht
  X journal   rood/oranje
  X flatly    groen
  X readable  wit
  X spacelab  blauw
  X united    donker rood/paars
  X lumen     wit
  X paper     licht blauw
  X sandstone bladgroen
  X simplex   bloedrood
  X yeti      blauwgroen
  darkly      pearle groen
  
### Frame X
  
  x
  
### Frame 1
  
```{r}
# add interactive bar -------
library(ggplot2)
library(ggiraph)

load(file="/home/fpadt/isdb/20-flexdashboards/x.Rdata")

# map the GV-colors 
#                    "-"      , MARA_EAN , PMDM_EAN , PMDM_GAN
gvColors        <- c(GV_ORNG_0, GV_GREY_1, GV_BLUE_2, GV_BLUE_0)
names(gvColors) <- levels(x$MAP)
colScale        <- scale_fill_manual(name = "pmdm", values = gvColors)
colScale_col    <- scale_color_manual(name = "pmdm", values = gvColors)

# Determine the breaks
db <- paste(ceiling(length(unique(x$Month))/9), "month")
br <- (1:10)/10
et <- element_text(
      family = "DejaVu Sans", face = "plain", colour = GV_GREY_1, size = 15)
at <- element_text(
      family = "DejaVu Sans", face = "plain", colour = GV_GREY_1, size = 12)


pQ <- 
  ggplot(data = x, mapping = aes(x = Month, y = Q, fill = MAP,
                                 tooltip = Q)) +
  colScale + 
  scale_x_date(date_breaks = eval(db), date_labels = "%Y.%m") +
  scale_y_continuous(sec.axis = sec_axis(~ . )) +
  # labs(title = paste0(params$opco ), x = "Date") +
  labs(
    title = opco_labels[OPCO == params$opco, LABEL], 
    subtitle = format(today(), "%A, %d %B, %Y "),
    x = "Date") +  
  facet_wrap(facets = "Category", nrow = 2) +
  theme(text = at, title = et, legend.position = "bottom")

pQI <- 
    pQ + 
    geom_col_interactive() +
    # geom_hline(
    #   data = x[, .(yintercept = mean(Q)), by = .(Category, MAP)], 
    #   mapping= aes(yintercept = yintercept, color = MAP)) +
    # colScale_col +
    labs(y = "Sell-Out Vol. ")
   

ggiraph(code = print(pQI))


```
  
*** 
    
Some commentary about Frame 1.
  
### Frame 2 {data-commentary-width=400}
  
```{r}
```
  
*** 
    
Some commentary about Frame 2.
  
# HQ {data-navmenu="Opco" data-icon="fa-pencil" data-orientation=rows}

# Swiss {data-navmenu="Opco" data-orientation=rows}

## ff

### Test2
This is not good
  
### Contact Rate

```{r}
rate <- 90
gauge(rate, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(80, 100), warning = c(40, 79), danger = c(0, 39)),
    href = "#Details"
)
```
  
### Average Rating 
  
```{r}
rating <- 30
gauge(rating, min = 0, max = 50, gaugeSectors(
  success = c(41, 50), warning = c(21, 40), danger = c(0, 20)
))
```
  
### Cancellations
  
```{r}
cancellations <- 8
gauge(cancellations, min = 0, max = 10, gaugeSectors(
  success = c(0, 2), warning = c(3, 6), danger = c(7, 10)
))
```
  
# Profiling {data-navmenu="Data"}
  
## col {data-height=400}
  
### Chart A
  
```{r fig.width=10, fig.height=7}
  hist(rnorm(n = 100, mean = 50, sd = 20))
```
  
### Value
```{r}
valueBox(1200, icon = "fa-pencil", href="http://www.grandvision.com")
```
  
### Spam
```{r}
spam <- 12
valueBox(spam, 
         icon = "fa-trash",
         color = ifelse(spam > 10, "warning", "primary"))
```
  
  
## col {.tabset .tabset-fade data-height=600}
  
### Chart B
  
```{r}
valueBox(1200, icon = "fa-pencil")
```
  
*** 
    
  Some commentary about Frame B on profiling.
  
### Chart C
  
```{r}
hist(rnorm(n = 100, mean = 50, sd = 20))
```
  
  > chart C
  
  
  
# Other {data-navmenu="Data" data-icon="fas fa-store" }
  
## col
  
### Chart A
  
```{r}
hist(rnorm(n = 100, mean = 50, sd = 20))
```
  
> chart A
  
## col {.tabset .tabset-fade}
  
### Chart B
  
```{r}
  hist(rnorm(n = 100, mean = 50, sd = 20))
```
  
> chart B
  
### Chart C
  
```{r}
  hist(rnorm(n = 100, mean = 50, sd = 20))
```
  
*** 
    
  Some commentary about Frame C on other.
  
# Details {.hidden}
  
  Hidden page for teh Gauge
  
  
  