---
title: "R Notebook"
output: html_notebook
---

```{r}
library(GGally)
library(data.table)
library(GGally)
library(ggplot2)

pth <- file.path("~", "..", "DS", "ENEXIS", "GIT", "data", "prep")
ffn <- file.path(pth, "Enexis_kleinverbruiksgegevens.csv" )
kvg <- fread(file.path(pth, "Enexis_decentrale_opwek_kv_(zon_pv).csv" ))
```
```{r}
f_c2d <- 
  function(x){
    sub(pattern = ",", replacement = "\\.", x = x ) %>%
      as.single()
  }

kvg[ , `:=` (fysieke_status_perc  = f_c2d(fysieke_status_perc ),
             lvr_richting_perc    = f_c2d(lvr_richting_perc ),
             sjv_gemiddeld        = f_c2d(sjv_gemiddeld ),
             sjv_laag_tarief_perc = f_c2d(sjv_laag_tarief_perc ),
             slimme_meter_perc    = f_c2d(slimme_meter_perc ),
             aansl_aantal         = f_c2d(aansl_aantal ),
             aansl_soort_perc     = f_c2d(aansl_soort_perc )
             )]


fwrite(kvg, file.path(pth, "Enexis_kleinverbruiksgegevens_key.csv" ) )

```


```{r}
# Create data 
 
# Check correlations (as scatterplots), distribution and print corrleation coefficient 
grp <- kvg[, .(aansl_opwek_aantal, opg_vermogen, aansl_cbs_aantal)]

gg <- ggpairs(
  data  = grp, 
  title = "correlogram Enexis",
  ) 
gg
ggsave(gg, path = "test.png")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
